### 2015-01-26 p3/submission.Rmd
add functions

From these plots, it appears that chlorides and sulphates have a small number of high outliers.  Residual sugar, however, appears to be long-tailed.  I'll instatiate a separate variable classifier, here, to annotate which wines are 'sweet'.  Using a (temporary) threshold of

```{r}
subset(df, residual.sugar > 45)
```

@@

```{r echo=FALSE}
grid.arrange(qplot(data = df, x = 'boxplot',
                   y = fixed.acidity,geom = 'boxplot'),
             qplot(data = df, x = 'boxplot',
                   y = volatile.acidity, geom = 'boxplot'),
             qplot(data = df, x = 'boxplot',
                   y = citric.acid, geom = 'boxplot'),
             qplot(data = df, x = 'boxplot',
                   y = TAC.acidity, geom = 'boxplot'),
             qplot(data = df, x = 'boxplot',
                   y = residual.sugar, geom = 'boxplot'),
             qplot(data = df, x = 'boxplot',
                   y = chlorides, geom = 'boxplot'),
             qplot(data = df, x = 'boxplot',
                   y = free.sulfur.dioxide, geom = 'boxplot'),
             qplot(data = df, x = 'boxplot',
                   y = total.sulfur.dioxide, geom = 'boxplot'),
             qplot(data = df, x = 'boxplot',
                   y = density, geom = 'boxplot'),
             qplot(data = df, x = 'boxplot',
                   y = pH, geom = 'boxplot'),
             qplot(data = df, x = 'boxplot',
                   y = sulphates, geom = 'boxplot'),
             qplot(data = df, x = 'boxplot',
                   y = alcohol, geom = 'boxplot'),
             ncol = 4)
```

@@

```{r echo=FALSE, Bivariate_Plots}
grid.arrange(qplot(data = df, x = quality,
                   y = fixed.acidity, geom = 'boxplot'),
             qplot(data = df, x = quality,
                   y = volatile.acidity, geom = 'boxplot'),
             qplot(data = df, x = quality,
                   y = citric.acid, geom = 'boxplot'),
             qplot(data = df, x = quality,
                   y = TAC.acidity, geom = 'boxplot'),
             qplot(data = df, x = quality,
                   y = log10(residual.sugar), geom = 'boxplot'),
             qplot(data = df, x = quality,
                   y = log10(chlorides), geom = 'boxplot'),
             qplot(data = df, x = quality,
                   y = free.sulfur.dioxide, geom = 'boxplot'),
             qplot(data = df, x = quality,
                   y = total.sulfur.dioxide, geom = 'boxplot'),
             qplot(data = df, x = quality,
                   y = density, geom = 'boxplot'),
             qplot(data = df, x = quality,
                   y = pH, geom = 'boxplot'),
             qplot(data = df, x = quality,
                   y = log10(sulphates), geom = 'boxplot'),
             qplot(data = df, x = quality,
                   y = alcohol, geom = 'boxplot'),
             ncol = 4)

grid.arrange(qplot(data = df, x = rating,
                   y = fixed.acidity, geom = 'boxplot'),
             qplot(data = df, x = rating,
                   y = volatile.acidity, geom = 'boxplot'),
             qplot(data = df, x = rating,
                   y = citric.acid, geom = 'boxplot'),
             qplot(data = df, x = rating,
                   y = TAC.acidity, geom = 'boxplot'),
             qplot(data = df, x = rating,
                   y = log10(residual.sugar), geom = 'boxplot'),
             qplot(data = df, x = rating,
                   y = log10(chlorides), geom = 'boxplot'),
             qplot(data = df, x = rating,
                   y = free.sulfur.dioxide, geom = 'boxplot'),
             qplot(data = df, x = rating,
                   y = total.sulfur.dioxide, geom = 'boxplot'),
             qplot(data = df, x = rating,
                   y = density, geom = 'boxplot'),
             qplot(data = df, x = rating,
                   y = pH, geom = 'boxplot'),
             qplot(data = df, x = rating,
                   y = log10(sulphates), geom = 'boxplot'),
             qplot(data = df, x = rating,
                   y = alcohol, geom = 'boxplot'),
             ncol = 4)
```

@@

```{r echo=FALSE}
correlations <- c(
cor.test(df$fixed.acidity, as.numeric(df$quality))$estimate,
cor.test(df$volatile.acidity, as.numeric(df$quality))$estimate,
cor.test(df$citric.acid, as.numeric(df$quality))$estimate,
cor.test(df$TAC.acidity, as.numeric(df$quality))$estimate,
cor.test(log10(df$residual.sugar), as.numeric(df$quality))$estimate,
cor.test(log10(df$chlorides), as.numeric(df$quality))$estimate,
cor.test(df$free.sulfur.dioxide, as.numeric(df$quality))$estimate,
cor.test(df$total.sulfur.dioxide, as.numeric(df$quality))$estimate,
cor.test(df$density, as.numeric(df$quality))$estimate,
cor.test(df$pH, as.numeric(df$quality))$estimate,
cor.test(log10(df$sulphates), as.numeric(df$quality))$estimate,
cor.test(df$alcohol, as.numeric(df$quality))$estimate)
names(correlations) <- c('fixed.acidity', 'volatile.acidity', 'citric.acid',
                         'TAC.acidity', 'log10.residual.sugar',
                         'log10.chlordies', 'free.sulfur.dioxide',
                         'total.sulfur.dioxide', 'density', 'pH',
                         'log10.sulphates', 'alcohol')
correlations
```

>>>>

From these plots, it appears that chlorides and sulphates have a small number of high outliers.

@@

```{r echo=FALSE}
get_simple_boxplot <- function(column) {
  return(qplot(data = df, x = 'simple',
               y = column, geom = 'boxplot',
               xlab = ''))
}

grid.arrange(get_simple_boxplot(df$fixed.acidity),
             get_simple_boxplot(df$volatile.acidity),
             get_simple_boxplot(df$citric.acid),
             get_simple_boxplot(df$TAC.acidity),
             get_simple_boxplot(df$residual.sugar),
             get_simple_boxplot(df$chlorides),
             get_simple_boxplot(df$free.sulfur.dioxide),
             get_simple_boxplot(df$total.sulfur.dioxide),
             get_simple_boxplot(df$density),
             get_simple_boxplot(df$pH),
             get_simple_boxplot(df$sulphates),
             get_simple_boxplot(df$alcohol),
             ncol = 4)
```

@@

```{r echo=FALSE, Bivariate_Plots}
get_bivariate_boxplot <- function(x, y, xlab, ylab) {
  return(qplot(data = df, x = x, y = y, geom = 'boxplot'))
}

grid.arrange(get_bivariate_boxplot(df$quality, df$fixed.acidity),
             get_bivariate_boxplot(df$quality, df$volatile.acidity),
             get_bivariate_boxplot(df$quality, df$citric.acid),
             get_bivariate_boxplot(df$quality, df$TAC.acidity),
             get_bivariate_boxplot(df$quality, log10(df$residual.sugar)),
             get_bivariate_boxplot(df$quality, log10(df$chlorides)),
             get_bivariate_boxplot(df$quality, df$free.sulfur.dioxide),
             get_bivariate_boxplot(df$quality, df$total.sulfur.dioxide),
             get_bivariate_boxplot(df$quality, df$density),
             get_bivariate_boxplot(df$quality, df$pH),
             get_bivariate_boxplot(df$quality, log10(df$sulphates)),
             get_bivariate_boxplot(df$quality, df$alcohol),
             ncol = 4)

grid.arrange(get_bivariate_boxplot(df$rating, df$fixed.acidity),
             get_bivariate_boxplot(df$rating, df$volatile.acidity),
             get_bivariate_boxplot(df$rating, df$citric.acid),
             get_bivariate_boxplot(df$rating, df$TAC.acidity),
             get_bivariate_boxplot(df$rating, log10(df$residual.sugar)),
             get_bivariate_boxplot(df$rating, log10(df$chlorides)),
             get_bivariate_boxplot(df$rating, df$free.sulfur.dioxide),
             get_bivariate_boxplot(df$rating, df$total.sulfur.dioxide),
             get_bivariate_boxplot(df$rating, df$density),
             get_bivariate_boxplot(df$rating, df$pH),
             get_bivariate_boxplot(df$rating, log10(df$sulphates)),
             get_bivariate_boxplot(df$rating, df$alcohol),
             ncol = 4)
```

@@

```{r echo=FALSE}
simple_cor_test <- function(x, y) {
  return(cor.test(x, y)$estimate)
}

correlations <- c(
  simple_cor_test(df$fixed.acidity, as.numeric(df$quality)),
  simple_cor_test(df$volatile.acidity, as.numeric(df$quality)),
  simple_cor_test(df$citric.acid, as.numeric(df$quality)),
  simple_cor_test(df$TAC.acidity, as.numeric(df$quality)),
  simple_cor_test(log10(df$residual.sugar), as.numeric(df$quality)),
  simple_cor_test(log10(df$chlorides), as.numeric(df$quality)),
  simple_cor_test(df$free.sulfur.dioxide, as.numeric(df$quality)),
  simple_cor_test(df$total.sulfur.dioxide, as.numeric(df$quality)),
  simple_cor_test(df$density, as.numeric(df$quality)),
  simple_cor_test(df$pH, as.numeric(df$quality)),
  simple_cor_test(log10(df$sulphates), as.numeric(df$quality)),
  simple_cor_test(df$alcohol, as.numeric(df$quality)))
names(correlations) <- c('fixed.acidity', 'volatile.acidity', 'citric.acid',
                         'TAC.acidity', 'log10.residual.sugar',
                         'log10.chlordies', 'free.sulfur.dioxide',
                         'total.sulfur.dioxide', 'density', 'pH',
                         'log10.sulphates', 'alcohol')
correlations
```
